Machine Learning Approach to Soccer Player's Overall Rating Prediction

### 2021-12-12 Paper/main.tex
Final version of main.tex

    To demonstrate the benefits of our model, we built various charts and evaluated it. In our experiments, neural networks could ... compared to liner regression.

@@

\section*{Results and Discussion}
\subsection*{Results}
We will use the best model from hyperparameter tuning to make predictions on the testing set and generate our final result. Our model has never seen the test set before, so this performance should be a good indicator of how the model would perform if deployed in the real world.

@@

>>>>

    To demonstrate the benefits of our model, we built various charts and evaluated it. In our experiments, we evaluate the performance of 5 different models, which are Linear Regression, Random Forest, Gradient Boosted, K-Nearest Neighbors and Neural Network. Finally, we choose the best model and the most useful model among all these models and discussed their different usages.

@@

\section*{Results and Discussion}
We will use the best model from hyperparameter tuning to make predictions on the testing set and generate our final result. Our model has never seen the test set before, so this performance should be a good indicator of how the model would perform if deployed in the real world.

@@

Invesgating these parameters, we have some interesting observations. The value of parameters can reflect the significance of an ability to a position. Below we take midfielders as an example.

We use Python's $heapq$ library to find the 5 largest coefficients and their corresponding attribute names of linear regression model for midfielders. The results are shown in the table below.

\begin{table}[htpb]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textit{Attribute Name}             &       \textit{Coefficient Value} \\ \hline
    \textit{BallControl}                &       \textit{0.24730435} \\ \hline
    \textit{ShortPassing}               &       \textit{0.18084552} \\ \hline
    \textit{Reactions}                  &       \textit{0.14724705} \\ \hline
    \textit{Dribbling}                  &       \textit{0.07184282} \\ \hline
    \textit{Age}                        &       \textit{0.06818059} \\ \hline
    \end{tabular}
    \caption{The 5 largest coefficients and their corresponding attribute names.}
\end{table}

From this table, we can observe that the main attributes contributing to a midfielder's overall rating are ball control, short passing, reactions and dribbling. This actually matches the reality, since normally a midfielder should control the ball and try to pass it to attacking players nearby. Besides, an older midfielder tends to have higher overall rating. This also shows that a midfielder with more experience is highly appreciated, since $Age$ also has a high coefficient value.

The attributes with high coefficients highly reflects the requirement of corresponding position. In this way, these information can be quite useful for soccer clubs to design suitable tactics or to improve their training for their own players. A soccer team can even use its own player data to train these coefficients, and inspect which attributes reflects the team's style, and then pay more attention to practicing on these aspects in their youth training.

In summary, neural network model performs a little bit better on accurately predicting overall ratings, while linear regression can provide more information about positions to soccer clubs. From our perspective, these 2 models can be used cooperatively for soccer clubs. Neural network can give accurate prediction for ratings to find potent players, and linear regression can be used to provide information for helping cultivating young players or planning tactics.
